Effects on projectivity ratings by Embedding Operator and Trigger --- \newline Data Analysis

### 2022-11-30 materials-lisa/analysis/3_projection-across-operators/analysis.Rnw
updated analysis files

glmm2a <- lmer(projective ~ verb * op + (1 | workerid) +
                 (1 | content), data=data)

# save.image("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
load("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
print(summary(glmm2a), cor=F, dig=3)

\subsection{Linear frequentist with \texttt{prove/n} as baseline}
<<freq-linear-annoyed-q, message=FALSE>>=

# dummy coding for "verb" with "prove" as baseline
data$verb <- relevel(data$verb, ref = "prove")

### dummy coding for "op" with "n" as baseline
data$op <- relevel(data$op, ref = "n")

# glmm3 <- lmer(projective ~ verb * op + (1 | workerid) +
#                  (1 | content), data=data)
# 
# save.image("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
load("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
print(summary(glmm3), cor=F, dig=3)

\subsection{Linear frequentist with \texttt{know/m} as baseline}
<<freq-linear-annoyed-q, message=FALSE>>=

@@

# glmm4 <- lmer(projective ~ verb * op + (1 | workerid) +
#                  (1 | content), data=data)
# 
# save.image("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
load("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
print(summary(glmm4), cor=F, dig=3)

>>>>

# glmm2a <- lmer(projective ~ verb * op + (1 | workerid) +
#                  (1 | content), data=data)

# save.image("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
# load("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
print(summary(glmm2a), cor=F, dig=3)

@
% 
% \subsection{Linear frequentist with \texttt{prove/n} as baseline}
% % <<freq-linear-prove-n, message=FALSE>>=
% # dummy coding for "verb" with "prove" as baseline
% data$verb <- relevel(data$verb, ref = "prove")
% 
% ### dummy coding for "op" with "n" as baseline
% data$op <- relevel(data$op, ref = "n")
% 
% # glmm3 <- lmer(projective ~ verb * op + (1 | workerid) +
% #                  (1 | content), data=data)
% #
% # save.image("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
% # load("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
% print(summary(glmm3), cor=F, dig=3)
% 
% @

\subsection{Linear frequentist with \texttt{know/m} as baseline}
<<freq-linear-know-m, message=FALSE>>=

@@

# glmm4 <- lmer(projective ~ verb * op + (1 | workerid) +
#                  (1 | content), data=data)
#
# save.image("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
# load("../../../results/main/meta-analyses/projectivity/rscripts/linear-models.RData")
print(summary(glmm4), cor=F, dig=3)
